\sysfull

### 2019-10-01 paper/TOSN/systemdescription.tex
comma removed after i.e.

\paragraph{Adaptive Task Scheduler.}
\sys's adaptive task scheduler (ATS) makes \emph{energy-aware} scheduling decisions to group tasks together or split a task. By coalescing tasks \sys \emph{amortizes commit and transition costs}, and by splitting a task, after it repeatedly failed to complete, it \emph{avoids the task non-termination problem}. The scheduler uses its recent execution history---i.e., it is hardware independent---as a metric to estimate energy availability and eventually to decide on the coalesced task size. Section~\ref{sec:task_adaptation} describes ATS.

>>>>

\paragraph{Adaptive Task Scheduler.}
\sys's adaptive task scheduler (ATS) makes \emph{energy-aware} scheduling decisions to group tasks together or split a task. By coalescing tasks \sys \emph{amortizes commit and transition costs}, and by splitting a task, after it repeatedly failed to complete, it \emph{avoids the task non-termination problem}. The scheduler uses its recent execution history---i.e. it is hardware independent---as a metric to estimate energy availability and eventually to decide on the coalesced task size. Section~\ref{sec:task_adaptation} describes ATS.
